---
title: "Lab 00 - Hello IDS!"
author: "Druvis Keiri"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Druvis Keiri", "Charlie Franklin-White", "Jami Burrell", 
           "Sean Wang", "Annie Loi","Duncan Hoyland"),
  github_username = c("squareheadge34", "cfranklinwhite", "jamie-burrell", 
                      "sw-005", "aaannniie","duncan-hoyland"), 
  colour = c("purple", "blue", "blue",
             "green", "blue","seagreen"),
  hobby = c("Basketball", "poker", "climbing", 
            "Gaming", "Gaming","rugby"),
  favourite_number = c(6, 2, 2, 8, 7, 2)
)

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The Graphic shows the different members of the group and their favorite number in the form of a bar graph.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github_username", 
          y = "Favourit_Number",
          title = "Favourite numbers Graph")
```

Labs stands for labels and will put titles/lables onto your graph.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
